Lasso_RCI_Response

### 2024-04-08 Lasso_RCI_Response.Rmd
Discriptive Satistics

## Create a TableOne object
table1_tab_anx <- CreateTableOne(vars = table1_vars_anx, data = Mothership_lasso,strata ="Anxiety_Responder",  factorVars = catVars)
table1_tab_anx <- print(table1_tab_anx, formatOptions = list(big.mark = ","))
table1_tab_anx <- data.frame(table1_tab_anx)
write_csv(table1_tab_anx,"~/Downloads/table1_tab_anx.csv")
table1_tab_anx
### next gather info based upon depression

@@

## Create a TableOne object
table1_tab_dep <- CreateTableOne(vars = table1_vars_dep, data = Mothership_lasso,strata ="Depression_Responder",  factorVars = catVars)
table1_tab_dep <- print(table1_tab_dep, formatOptions = list(big.mark = ","))
table1_tab_dep <-data.frame(table1_tab_dep)
write_csv(table1_tab_dep,"~/Downloads/table1_tab_dep.csv")
table1_tab_dep

@@

mean(Mothership_lasso$CUDOS_pre)
sd(Mothership_lasso$CUDOS_pre)
mean(Mothership_lasso$CUDOS_post)
sd(Mothership_lasso$CUDOS_post)

>>>>

## Create a TableOne object
table1_tab_anx <- CreateTableOne(vars = table1_vars_anx, data = Mothership_lasso,strata ="Anxiety_Responder",  factorVars = catVars)
table1_tab_anx <- print(table1_tab_anx, formatOptions = list(big.mark = ","))
table1_tab_anx <- data.frame(table1_tab_anx)
table1_tab_anx<- table1_tab_anx[-2,]
write_csv(table1_tab_anx,"~/Downloads/table1_tab_anx.csv")
table1_tab_anx
```

```{r}
### next gather info based upon depression

@@

## Create a TableOne object
table1_tab_dep <- CreateTableOne(vars = table1_vars_dep, data = Mothership_lasso,strata ="Depression_Responder",  factorVars = catVars)
table1_tab_dep <- print(table1_tab_dep, formatOptions = list(big.mark = ","))
table1_tab_dep <-data.frame(table1_tab_dep)
table1_tab_dep <- table1_tab_dep[-2,]

# add discriptive statistics 
table1_tab_dep$ef_size = c("")

# age
table1_tab_dep[2,4] <- round(t_test(Age_1 ~ Depression_Responder, data = Mothership_lasso)$statistic,2)
table1_tab_dep[2,5] <- round(cohens_d(Age_1 ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
# Some College 
table1_tab_dep[3,4] <- round(chisq.test(Mothership_lasso$Some_College, Mothership_lasso$Depression_Responder)$statistic,2)
table1_tab_dep[3,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Some_College))$estimate,2)
# Female
table1_tab_dep[4,4] <- round(chisq.test(Mothership_lasso$Female, Mothership_lasso$Depression_Responder)$statistic,2)
table1_tab_dep[4,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Female))$estimate,2)
# Married
table1_tab_dep[5,4] <- round(chisq.test(Mothership_lasso$Married, Mothership_lasso$Depression_Responder)$statistic,2)
table1_tab_dep[5,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Married))$estimate,2)
# White
table1_tab_dep[6,4] <- round(chisq.test(Mothership_lasso$White, Mothership_lasso$Depression_Responder)$statistic,2)
table1_tab_dep[6,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$White))$estimate,2)
# Treatment track
table1_tab_dep[7,4] <- round(chisq.test(Mothership_lasso$IPT_track_1, Mothership_lasso$Depression_Responder)$statistic,2)
# OR general vs Trauma track
table1_tab_dep[9,5] <- round(fisher.test(cbind(OR_IPT_Tab[,"General"],OR_IPT_Tab[,"Trauma"]))$estimate,2)
# OR General vs Young adult track 
table1_tab_dep[10,5] <- 
  round(fisher.test(cbind(OR_IPT_Tab[,"General"],OR_IPT_Tab[,"Young Adult"]))$estimate,2)
# Days Completed in program
table1_tab_dep[11,4] <- round(t_test(Days_complete_1 ~ Depression_Responder, data = Mothership_lasso)$statistic,2)
round(table1_tab_dep[11,5] <- cohens_d(Days_complete_1 ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
# Days not attending treatment
table1_tab_dep[12,4] <- round(t_test(Days_not_attended_1 ~ Depression_Responder, data = Mothership_lasso)$statistic,2)
round(table1_tab_dep[12,5] <- cohens_d(Days_not_attended_1 ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
# Anxiety disorder
table1_tab_dep[13,4] <- round(chisq.test(Mothership_lasso$Anxiety_D, Mothership_lasso$Depression_Responder)$statistic,2)
table1_tab_dep[13,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Anxiety_D))$estimate,2)
table1_tab_dep[14,4] <- round(chisq.test(Mothership_lasso$Mood_D, Mothership_lasso$Depression_Responder)$statistic,2)
table1_tab_dep[14,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Mood_D))$estimate,2)
# BPD 
table1_tab_dep[15,4] <- round(chisq.test(Mothership_lasso$BPD_P, Mothership_lasso$Depression_Responder)$statistic,2)
table1_tab_dep[15,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$BPD_P))$estimate,2)
# Truama Related Disorders
table1_tab_dep[16,4] <- round(chisq.test(Mothership_lasso$Trauma_D, Mothership_lasso$Depression_Responder)$statistic,2)
table1_tab_dep[16,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Trauma_D))$estimate,2)
# Other Disorders
table1_tab_dep[17,4] <- round(chisq.test(Mothership_lasso$Other, Mothership_lasso$Depression_Responder)$statistic,2)
table1_tab_dep[17,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Other))$estimate,2)
# Co-occurring anxiety disorder 
table1_tab_dep[18,4] <- round(chisq.test(Mothership_lasso$Anxiety_C, Mothership_lasso$Depression_Responder)$statistic,2)
table1_tab_dep[18,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Anxiety_C))$estimate,2)
# Co-occurring mood disorder
table1_tab_dep[19,4] <- round(chisq.test(Mothership_lasso$Mood_C, Mothership_lasso$Depression_Responder)$statistic,2)
table1_tab_dep[19,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Mood_C))$estimate,2)
# Co-occurring BPD
table1_tab_dep[20,4] <- round(chisq.test(Mothership_lasso$BPD_Co_C, Mothership_lasso$Depression_Responder)$statistic,2)
table1_tab_dep[20,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$BPD_Co_C))$estimate,2)
# Co-occurring Trauma Related Disorder
table1_tab_dep[21,4] <- round(chisq.test(Mothership_lasso$Trauma_C, Mothership_lasso$Depression_Responder)$statistic,2)
table1_tab_dep[21,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Trauma_C))$estimate,2)
# Co-occurring Substance Use Disorders
table1_tab_dep[22,4] <- round(chisq.test(Mothership_lasso$Substance_C, Mothership_lasso$Depression_Responder)$statistic,2)
table1_tab_dep[22,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Substance_C))$estimate,2)
# Co-occurring Other Disroders
table1_tab_dep[23,4] <- round(chisq.test(Mothership_lasso$Other_C, Mothership_lasso$Depression_Responder)$statistic,2)
table1_tab_dep[23,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Other_C))$estimate,2)
# No Co-occurring Disorders
table1_tab_dep[24,4] <- round(chisq.test(Mothership_lasso$No_Co, Mothership_lasso$Depression_Responder)$statistic,2)
table1_tab_dep[24,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$No_Co))$estimate,2)
# Number of Current diagnoses 
table1_tab_dep[25,4] <- round(t_test(Current_Dx ~ Depression_Responder, data = Mothership_lasso)$statistic,2)
table1_tab_dep[25,5] <- round(cohens_d(Current_Dx ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
# CUDOS Pre scores
table1_tab_dep[26,4] <- round(t_test(CUDOS_pre ~ Depression_Responder, data = Mothership_lasso)$statistic,2)
table1_tab_dep[26,5] <- round(cohens_d(CUDOS_pre ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
# CUXOS Pre scores
table1_tab_dep[27,4] <- round(t_test(CUXOS_pre ~ Depression_Responder, data = Mothership_lasso)$statistic,2)
table1_tab_dep[27,5] <- round(cohens_d(CUXOS_pre ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
# RDQ Coping post scores
table1_tab_dep[28,4] <- round(t_test(rdqPOST_coping ~ Depression_Responder, data = Mothership_lasso)$statistic,2)
table1_tab_dep[28,5] <- round(cohens_d(rdqPOST_coping ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
# RDQ Positive Mental Health post scores
table1_tab_dep[29,4] <- round(t_test(rdqPOST_pmh ~ Depression_Responder, data = Mothership_lasso)$statistic,2)
table1_tab_dep[29,5] <- round(cohens_d(rdqPOST_pmh ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
# RDQ Functioning post scores
table1_tab_dep[30,4] <- round(t_test(rdqPOST_func ~ Depression_Responder, data = Mothership_lasso)$statistic,2)
table1_tab_dep[30,5] <- round(cohens_d(rdqPOST_func ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
# RDQ Sense of Wellbeing post scores
table1_tab_dep[31,4] <- round(t_test(rdqPOST_wbs ~ Depression_Responder, data = Mothership_lasso)$statistic,2)
table1_tab_dep[31,5] <- round(cohens_d(rdqPOST_wbs ~ Depression_Responder, data = Mothership_lasso)$effsize,2)

table1_tab_dep
write_csv(table1_tab_dep,"~/Downloads/table1_tab_dep.csv")

```{r}

@@
